Summary Tables

### 2022-10-26 summary_tables.Rmd
Use cities from cities var and set the scenario name

```{r load_objects = "asis", echo = F, message = F}
io <- readRDS("results/multi_city/io.rds")
# Assumes that multi_city_script.R has been run till 
# Get names of cities from the io object
cities <- names(io)[!names(io) %in% 'scen_prop']
LATAM <- F
AFRICA_INDIA = T
NSCEN <- nrow(io$scen_prop)
#cities <- c('accra','sao_paulo','buenos_aires')

@@

## Case study specific propensities
```{r message=F, error=F, warning=FALSE}
get_scen_settings <- ithimr::get_scenario_settings()

@@

    } # Loop for each city
  } # Loop for each pathway
} # Loop for each measure
# # Export deaths HB
# path_deaths_wb <- "results/multi_city/health_impacts/Deaths.xlsx"
# deaths_wb <- readWorkbook(path_deaths_wb)
# wb <-  loadWorkbook(path_deaths_wb)
# removeTable(wb = wb, sheet = "Deaths", table = "Tabla1")
# writeDataTable(wb, sheet = "Deaths", x = rbindlist(health$deaths$hb, use.names = T), tableName = "Tabla1", startCol = 1)
# removeTable(wb = wb, sheet = "Deaths_Pathway", table = "Tabla2")
# writeDataTable(wb, sheet = "Deaths_Pathway", x = rbindlist(health$deaths$pathway_hb, use.names = T), tableName = "Tabla2", startCol = 1)
# saveWorkbook(wb, path_deaths_wb, overwrite =TRUE)
# 
# # Export ylls HB
# path_ylls_wb <- "results/multi_city/health_impacts/YLLs.xlsx"
# ylls_wb <- readWorkbook(path_ylls_wb)
# wb <-  loadWorkbook(path_ylls_wb)
# removeTable(wb = wb, sheet = "YLLs", table = "Tabla1")
# writeDataTable(wb, sheet = "YLLs", x = rbindlist(health$ylls$hb, use.names = T), tableName = "Tabla1", startCol = 1)
# removeTable(wb = wb, sheet = "YLLs_Pathway", table = "Tabla2")
# writeDataTable(wb, sheet = "YLLs_Pathway", x = rbindlist(health$ylls$pathway_hb, use.names = T), tableName = "Tabla2", startCol = 1)
# saveWorkbook(wb, path_ylls_wb, overwrite =TRUE)
#

# Remove CIs
ylls <-  rbindlist(health$ylls$hb, use.names = T) |> filter(!str_detect(cause, "_lb") & !str_detect(cause, "_ub"))
ylls_pathway <- rbindlist(health$ylls$pathway_hb, use.names = T) |> filter(!str_detect(cause, "_lb") & !str_detect(cause, "_ub"))
deaths <- rbindlist(health$deaths$hb, use.names = T)|> filter(!str_detect(cause, "_lb") & !str_detect(cause, "_ub"))
deaths_pathway <- rbindlist(health$deaths$pathway_hb, use.names = T) |> filter(!str_detect(cause, "_lb") & !str_detect(cause, "_ub"))

# Export ylls HB
output_file <- "results/multi_city/health_impacts/data.xlsx"
writexl::write_xlsx(list(ylls = ylls,
                         ylls_pathway = ylls_pathway,
                         deaths = deaths,
                         deaths_pathway = deaths_pathway), 
                    path = output_file)

# Export ylls HB
write.csv(ylls,
            "results/multi_city/health_impacts/ylls.csv",
            row.names = F)
# Export ylls PATHWAY_HB
write.csv(ylls_pathway,
            "results/multi_city/health_impacts/ylls_pathway.csv",
            row.names = F)
# Export deaths HB
write.csv(deaths,
            "results/multi_city/health_impacts/deaths.csv",
            row.names = F)
# Export deaths PATHWAY_HB
write.csv(deaths_pathway,
            "results/multi_city/health_impacts/deaths_pathway",
            row.names = F)

>>>>

```{r load_objects = "asis", echo = F, message = F}
io <- readRDS("results/multi_city/io.rds")
# Assumes that multi_city_script.R has been run till 
# Get names of cities from the io object
cities <- names(io)[!names(io) %in% 'scen_prop']
LATAM <- F
AFRICA_INDIA = F
GLOBAL <- T
NSCEN <- nrow(io$scen_prop)
#cities <- c('accra','sao_paulo','buenos_aires')

@@

## Case study specific propensities
```{r message=F, error=F, warning=FALSE}
get_scen_settings <- ithimr::get_scenario_settings(cities = cities)

@@

    } # Loop for each city
  } # Loop for each pathway
} # Loop for each measure
# # Export deaths HB
# path_deaths_wb <- "results/multi_city/health_impacts/Deaths.xlsx"
# deaths_wb <- readWorkbook(path_deaths_wb)
# wb <-  loadWorkbook(path_deaths_wb)
# removeTable(wb = wb, sheet = "Deaths", table = "Tabla1")
# writeDataTable(wb, sheet = "Deaths", x = rbindlist(health$deaths$hb, use.names = T), tableName = "Tabla1", startCol = 1)
# removeTable(wb = wb, sheet = "Deaths_Pathway", table = "Tabla2")
# writeDataTable(wb, sheet = "Deaths_Pathway", x = rbindlist(health$deaths$pathway_hb, use.names = T), tableName = "Tabla2", startCol = 1)
# saveWorkbook(wb, path_deaths_wb, overwrite =TRUE)
# 
# # Export ylls HB
# path_ylls_wb <- "results/multi_city/health_impacts/YLLs.xlsx"
# ylls_wb <- readWorkbook(path_ylls_wb)
# wb <-  loadWorkbook(path_ylls_wb)
# removeTable(wb = wb, sheet = "YLLs", table = "Tabla1")
# writeDataTable(wb, sheet = "YLLs", x = rbindlist(health$ylls$hb, use.names = T), tableName = "Tabla1", startCol = 1)
# removeTable(wb = wb, sheet = "YLLs_Pathway", table = "Tabla2")
# writeDataTable(wb, sheet = "YLLs_Pathway", x = rbindlist(health$ylls$pathway_hb, use.names = T), tableName = "Tabla2", startCol = 1)
# saveWorkbook(wb, path_ylls_wb, overwrite =TRUE)
# # Export ylls HB
output_file <- "results/multi_city/health_impacts/data.xlsx"
writexl::write_xlsx(list(ylls_hb_lng = rbindlist(health$ylls$hb, use.names = T),
                         ylls_pathway_hb_lng = rbindlist(health$ylls$pathway_hb, use.names = T),
                         Deaths = rbindlist(health$deaths$hb, use.names = T),
                         Deaths_Pathway = rbindlist(health$deaths$pathway_hb, use.names = T)), path = output_file)

# Export ylls HB
write.csv(rbindlist(health$ylls$hb, use.names = T),
            "results/multi_city/health_impacts/ylls_hb_lng.csv",
            row.names = F)
# Export ylls PATHWAY_HB
write.csv(rbindlist(health$ylls$pathway_hb, use.names = T),
            "results/multi_city/health_impacts/ylls_pathway_hb_lng.csv",
            row.names = F)
# Export deaths HB
write.csv(rbindlist(health$deaths$hb, use.names = T),
            "results/multi_city/health_impacts/deaths_hb_lng.csv",
            row.names = F)
# Export deaths PATHWAY_HB
write.csv(rbindlist(health$deaths$pathway_hb, use.names = T),
            "results/multi_city/health_impacts/deaths_pathway_hb_lng.csv",
            row.names = F)
